### 2019-01-19 1-Preamble/4-Acknowledgement/acknowledgement.tex
Cosmetic change + first version of the acknowledgements (yes, it's useless to write this first… I know)

And I would like to acknowledge ...

See https://perso.crans.org/besson/phd/thanks/

\TODO{To start!}

>>>>

\TODO{To finish}
% See https://perso.crans.org/besson/phd/thanks/

And I would like to acknowledge and thank the following people.

My PhD advisors, \href{https://moychristophe.wordpress.com/}{Christophe Moy} and \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{Émilie Kaufmann}.

My family: my parents, my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother} and my younger brother, Marine, my grand-parents, Jacques, Bernadette, Lara.

My closest friends, in a chronological list: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia, Julia, Pierre, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément, Jill-Jênn, Alain, Claire, Édouard, Loïc, Damien, Kumudham, Priscilla, Thibault, Sébastien, Sélim, Valentin, Marine, Johanne, Lola.

My wonderful colleagues during these three years: Rémi, Pascal, Yves, Jacques, Ali, Haïfa, Marwa, Navik, Quentin, Vincent, Rami, Cristo, Adrien, Esteban, Ali, Éloïse, Bastien, Pierre, Georgios, in Rennes; and Ronan, Odalric-Ambrym, Philippe, Olivier, Florian, Xuedong, Guillaume, Julien, Mathieu, Matteo, Mahsa, Nicolas in Lille.

Thanks to some people for their support: Karine, Jeannine, Greg, Anne at CentraleSupélec Rennes, François, David and David at ENS de Rennes, Romaric at ENSAI, Amélie at Inria Lille, Frédéric, Alain, Sylvain, Paul, Serge, Claudine, Nicolas, Carine and Delphine at ENS Cachan (now Paris-Saclay).

I would also like to thank some things. First, the Earth, then my \href{https://perso.crans.org/besson/zero-dechet/}{bike} which I enjoyed riding everyday despite the too many accidents.
My \href{https://perso.crans.org/besson/cuisine/}{culinary friends}: cheese, chocolate, coffee, vegetables etc!
My \href{https://perso.crans.org/besson/}{technological friends}: Bash, Python, XUbuntu, Firefox, Konsole, Visual Studio Code etc.

Some friends thanked me in their own PhD thesis, and it is a pleasure to do the same!
%
\begin{itemize}
\tightlist
\item
  \href{http://jill-jenn.net/}{Jill-Jênn Vie}
  (\href{http://jiji.cat/cat.pdf}{thesis})
\item
  \href{https://navikkumarmodi.wordpress.com/}{Navikkumar Modi}
  (\href{https://tel.archives-ouvertes.fr/tel-01668536/document}{thesis})
\item
  \href{https://quentinbodinier.wordpress.com/}{Quentin Bodinier}
  (\href{https://www.theses.fr/2017REN1S091}{thesis})
\item
  \href{https://paris-sorbonne.academia.edu/FBesson}{Florian Besson}
\item
  \href{https://sites.google.com/view/guerand}{Jessica Guérand}
  (\href{https://drive.google.com/open?id=17CBibM8ZlzIbyVxpxktK3j5rNePALUs8}{thesis})
\item
  \href{https://sites.google.com/view/ducasse/}{Romain Ducasse}
\item
  \href{https://members.loria.fr/SAbelard/}{Simon Abelard}
  (\href{https://members.loria.fr/SAbelard/theseabelard.pdf}{thesis})
\item
  \href{http://www.cmap.polytechnique.fr/~sacchelli/}{Ludovic Sacchelli}
\item
  \href{http://pages.saclay.inria.fr/claire.brecheteau/}{Claire
  Brécheteau}
  (\href{https://hal.archives-ouvertes.fr/tel-01897787/document}{thesis})
\item
  \href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/}{Damien
  Allonsius}
  (\href{http://www.i2m.univ-amu.fr/perso/damien.allonsius/documents/recherche/these/Main.pdf}{thesis})
\item
  \href{https://remibonnefoi.wordpress.com/}{Rémi Bonnefoi}
\item
  \href{https://remibonnefoi.wordpress.com/}{Rami Othman}
\end{itemize}

% Je souhaite terminer ces remerciements par une pensée toute particulière pour Lola, qui m'a soutenu, qui m'a émerveillé par son enthousiasme et qui m'a réconforté par son amour durant la dernière année.
Deseo terminar este agradecimiento con un pensamiento especial para Lola, quien me apoyó, me sorprendió con su entusiasmo y me consoló con su amor durante el año pasado.
